### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/backmatter.tex
sort Ty's contribution and correct title (I think)

\authorcontributions{Conceptualization, B.L., M.W., C.S. and T.N.; methodology, B.L., M.W., C.S., T.N. and B.L.; software, B.W.; validation, B.L and M.W.; formal analysis, B.W.; investigation, B.W.; resources, M.W. and B.L.; data curation, B.W.; writing---original draft preparation, B.W.; writing---review and editing, B.L. and M.W.; visualization, B.W.; supervision, M.W and B.L.; project administration, B.L.; funding acquisition, B.L, M.W, C.S and T.N. All authors have read and agreed to the published version of the manuscript.}

>>>>

\authorcontributions{Conceptualization, B.L., M.W., C.S. and T.N.; methodology, B.W., M.W., C.S., T.N. and B.L.; software, B.W.; validation, B.L and M.W.; formal analysis, B.W.; investigation, B.W.; resources, M.W. and B.L.; data curation, B.W.; writing---original draft preparation, B.W.; writing---review and editing, B.L., M.W. and T.N.; visualization, B.W.; supervision, M.W and B.L.; project administration, B.L.; funding acquisition, B.L, M.W, C.S and T.N. All authors have read and agreed to the published version of the manuscript.}
